How did local health infrastructure and socio-political factors within different states and counties in the United States affect the disparities in COVID-19 outcomes, and what lessons can be learned for more targeted public health preparedness and response strategies in future pandemics?

### 2024-02-13 outputs/paper/paper.qmd
changes

---
title: "How did local health infrastructure and socio-political factors within different states and counties in the United States affect the disparities in COVID-19 outcomes, and what lessons can be learned for more targeted public health preparedness and response strategies in future pandemics?"
author: 
  - Adrian Ly
  - Sakhil Goel
  - Hannah Yu
thanks: "Code and data are available at: https://github.com/hannahyu07/US-Covid-Analysis.git"
date: today
date-format: long
abstract: "In this research, we explored the complex interplay between local health infrastructure, socio-political factors, and COVID-19 outcomes across various U.S. states and counties to understand disparities in the pandemic's impact. Our findings reveal that political polarization and healthcare access disparities significantly influenced adherence to health guidelines and the effectiveness of the public health response. Additionally, social vulnerabilities and inconsistent public health messaging further exacerbated the pandemic's impact on marginalized communities. This study underscores the critical need for targeted public health strategies that address socio-political and infrastructural disparities to enhance pandemic preparedness and response, emphasizing the importance of equity and effective communication in safeguarding public health."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "How did local health infrastructure and socio-political factors within different states and counties in the United States affect the disparities in COVID-19 outcomes, and what lessons can be learned for more targeted public health preparedness and response strategies in future pandemics?"
author: 
  - Adrian Ly
  - Hannah Yu
thanks: "Code and data are available at: https://github.com/hannahyu07/US-Covid-Analysis.git"
date: today
date-format: long
abstract: "In this research, we explored the complex interplay between local health infrastructure, socio-political factors, and COVID-19 outcomes across various U.S. states and counties to understand disparities in the pandemic's impact. Our findings reveal that political polarization and healthcare access disparities significantly influenced adherence to health guidelines and the effectiveness of the public health response. Additionally, social vulnerabilities and inconsistent public health messaging further exacerbated the pandemic's impact on marginalized communities. This study underscores the critical need for targeted public health strategies that address socio-political and infrastructural disparities to enhance pandemic preparedness and response, emphasizing the importance of equity and effective communication in safeguarding public health."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
